Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-04 main.tex
minor polishment in first few sections

In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero. We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants. In particular, we take the opportunity to discuss bounded convex domains as a special case. This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.

@@

% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators.

We survey variations of the Poincar\'e and Poincar\'e--Friedrichs inequalities. 
We take the opportunity to discuss bounded convex domains as a preparatory special case.
This survey, which we believe to be of independent interest, will serve as a building block in constructing inequalities over triangulated domains.
\\

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\grad,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.

Because $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$,
any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    \leq 
    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{{\rm P}} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{{\rm P}}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{\varnothing,\Omega,p}$.

@@

\subsection{A triangulation or a simplicial complex}

@@

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*} % First pair 
        \matnorm{ \Jacobian \varphi } 
        \leq 
        \Ceins{n} \cdot \diam(T),
        \qquad 
        \matnorm{ \Jacobian \varphi^{-1} } 
        \leq 
        \Czwei{n} \cdot \aspectratio(T) \height(T)^{-1}
        ,
        \\
        \frac{1}{\sqrt{2n}} \aspectratio(T) \leq \algebraicshapemeasure(T) \leq n \aspectratio(T).
    \end{gather*}
    Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
\end{lemma}
\begin{proof}
    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine transformation. 
	We abbreviate $M := \Jacobian\phi$ for its Jacobian. 
    We begin with observing that the largest $\ell^{2}$-norm of any column of $M$,
    which here denote by $c_{\max}(M)$, 
    equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
    We also know that the diameter of $T$ is the length of its longest edge. 
    Our first pair of inequalities follows via standard comparisons of Euclidean norms:
    \begin{align*}
        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} c_{\max}(M) \leq \sqrt{n} \diam(T).
    \end{align*}
    The columns of the matrix $M^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
    except for the vertex $\varphi(0)$. It immediately follows that 
    \begin{align*}
        \matnorm{ M^{-1} } \leq \sqrt{n} c_{\max}(M^{-1}) \leq \sqrt{n} \cdot \height(T)^{-1}
        .
    \end{align*}
    The smallest height in the reference simplex $\Delta^{n}$ is $\height_{\Delta} = 1/\sqrt{n}$, 
    whence $\height(T) \geq \matnorm{M^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)$.
    All relevant results follow.
\end{proof}

We are interested in the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of the diameters of any intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}\label{math:volumeratio}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
\end{align}
\begin{align}\label{math:diameterratio}
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We then define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \matnorm{ \Jacobian \Xi_{T,T'} }
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

\cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
\begin{gather*}
    W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}}
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
\begin{gather*}
    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
We also introduce 
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align*}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align*}
\end{subequations}
Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
These transformations are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below. 
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
    \\
    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
    \\
    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
\end{align}
\end{subequations}
where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
    \end{CD}
\end{align*}

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
whose support lies in the open ball $B_r(x)$
we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$. We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega)$.

@@

\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}}

@@

\subsection{\cye{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}}

>>>>

\mwl{
In this section, we wish to explain why we employ linear potential operators to estimate the Poincar\'e--Friedrichs constants and we also address the difference of the Poincar\'e--Friedrichs inequality~\eqref{math:PF_gradient_2} with the Poincar\'e inequality where the mean value of $u$ is fixed to zero. We then review Poincar\'e--Friedrichs inequalities in the gradient case setting of Section~\ref{section:intro_grad}, with the emphasis on know results on analytical upper bounds for the constants. In particular, we take the opportunity to discuss bounded convex domains as a special case. 
This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.

@@

% Our particular notion of Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators. 
}

This section surveys variations of the Poincar\'e--Friedrichs inequalities for the gradient operator,
with emphasis on analytical upper bounds over bounded convex domains. 
We explain the difference between the Poincar\'e--Friedrichs inequality, which addresses the norm-minimizing potential, and the Poincar\'e inequality, which addresses the potential with mean value zero, and rephrase this in terms of potential operators. 
This survey serves as a building block in constructing computable constants over triangulated domains in a combinatorial way below but we believe it is also of independent interest.
\\

@@

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ u \in W^{1,p}(\Omega) \\ \nabla u = \bff } } \| u \|_{L^{p}(\Omega)},
    \quad 
    \forall 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
If there is a Poincar\'e--Friedrichs constant, then by definition
\begin{align*}
    \| \Phi(\bff) \|_{L^{p}(\Omega)} \leq C_{\grad,\Omega,p} \| \bff \|_{L^{p}(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{\grad,\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$.

Because $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ is generally a nonlinear operator for $p \neq 2$,
any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    \leq 
    \max\limits_{ u \in W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla u) \|_{L^{p}(\Omega)} }{ \| \nabla u \|_{L^{p}(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
    \quad 
    \forall 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the optimal Poincar\'e constant $C_{\varnothing,\Omega,p}$.

@@

% \subsection{A triangulation or a simplicial complex}

@@

\begin{lemma}\label{lemma:measurerelationships}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*} % First pair 
        \matnorm{ \Jacobian \varphi } 
        \leq 
        \Ceins{n} \cdot \diam(T),
        \qquad 
        \matnorm{ \Jacobian \varphi^{-1} } 
        \leq 
        \Czwei{n} \cdot \aspectratio(T) \height(T)^{-1}
        ,
        \\
        \frac{1}{\sqrt{2n}} \aspectratio(T) \leq \algebraicshapemeasure(T) \leq n \aspectratio(T).
    \end{gather*}
    Here, $\Ceins{n} = \Czwei{n} = \sqrt n$. 
\end{lemma}
\begin{proof}
    Let $\varphi : \Delta^{n} \rightarrow T$ be an affine transformation. 
	We abbreviate $M := \Jacobian\phi$ for its Jacobian. 
    We begin with observing that the largest $\ell^{2}$-norm of any column of $M$,
    which here denote by $c_{\max}(M)$, 
    equals the maximum of the quotient $\| M x \|_{\ell^{2}} / \| x \|_{\ell^{1}}$ over all non-zero $x \in \bbR^{n}$. 
    We also know that the diameter of $T$ is the length of its longest edge. 
    Our first pair of inequalities follows via standard comparisons of Euclidean norms:
    \begin{align*}
        \frac{\diam(T)}{\sqrt 2} \leq \matnorm{ M } \leq \sqrt{n} \cdot c_{\max}(M) \leq \sqrt{n} \cdot \diam(T).
    \end{align*}
    The columns of the matrix $M^{-1}$ are the gradients of the barycentric coordinates of the vertices of $T$,
    except for the vertex $\varphi(0) \in T$. It immediately follows that 
    \begin{align*}
        \matnorm{ M^{-1} } \leq \sqrt{n} c_{\max}(M^{-1}) \leq \sqrt{n} \cdot \height(T)^{-1}
        .
    \end{align*}
    The smallest height in the reference simplex $\Delta^{n}$ is $\height_{\Delta} = 1/\sqrt{n}$, 
    whence $\height(T) \geq \matnorm{M^{-1}}^{-1} / \sqrt{n}$. This yields our second pair of inequalities. 
    Notice that $\height(T)^{-1} \leq \aspectratio(T) \diam(T)^{-1}$.
    All relevant results follow.
\end{proof}

We will need the maximal ratio of volumes between face-neighboring $n$-simplices, written $\volumeratio(\calT)$,
and the ratio of the diameters of any intersecting simplices, written $\diameterratio(\calT)$. Formally, 
\begin{align}\label{math:volumeratio}
    \volumeratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } 
    \frac{ \vol(T) }{ \vol(T') }
    ,
\end{align}
\begin{align}\label{math:diameterratio}
    \diameterratio(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
    .
\end{align}
Finally, whenever $T, T'$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{T,T'} : T \rightarrow T'$ denote the affine diffeomorphism 
that preserves $F$. We then define 
\begin{align}\label{math:reflectionmeasure}
    \reflectionestimate(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \matnorm{ \Jacobian \Xi_{T,T'} }
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

% \cye{Recall the notations~\eqref{equation:W1p} and~\eqref{equation:W_curl_div_p} from Section~\ref{section:intro}; actually, here we temporarily rather employ 
% \begin{gather*}
    % W^{p}(\grad,\Omega) \cye{= W^{1,p}(\Omega)} = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    % .
% \end{gather*}}
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
We recall $L^{p}(\Omega)$, the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
\begin{gather*}
    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
\mwl{We introduce the} gradient-, curl-, and divergence-conforming Piola transformations, respectively, as the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, and 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$.
We also introduce 
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align*}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align*}
\end{subequations}
Here, $\Jacobian\phi$ is the Jacobian matrix of $\phi$ (see also~\cite[Definition~9.8]{ern2021finite}), and $\adj\Jacobian\phi$ denotes taking its adjugate matrix.
These transformations are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below. 
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
    \\
    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
    \\
    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
\end{align}
\end{subequations}
where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
    \end{CD}
\end{align*}

@@

Let us now turn our attention to Sobolev spaces of differential forms. 
Since the exterior product space $\Alt^{k}(\bbR^{n})$ carries a norm, induced from the Euclidean norm on $\bbR^{n}$, there are pointwise norms of differential $k$-forms. 
We let $L^{p}\Alt^{k}(\Omega)$ be the space of differential $k$-forms over $\Omega$ with locally integrable coefficients 
such that its pointwise norm is $p$-integrable. 
The exterior derivative is defined in the sense of distributions and we introduce 
\begin{gather*}
    W^{p}\Alt^{k}(\Omega) 
    := 
    \{ u \in L^{p}\Alt^{k}(\Omega) \suchthat \cartan u \in L^{p}\Alt^{k+1}(\Omega) \}
    .
\end{gather*}
We observe that $u \in L^{p}\Alt^{k}(\Omega)$ has weak exterior derivative $f \in L^{p}\Alt^{k+1}(\Omega)$
if and only if for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$ we have the integration by parts formula
\begin{align*}
    \int_{\Omega} \cartan v \wedge u
    &=
    (-1)^{k(n-k)+1}
    \int_{\Omega} v \wedge f 
    .
\end{align*}
% \mwl{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$.
% The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}
% \cye{\sout{We let $W^{p}_{0}\Alt^{k}(\Omega)$ be the closed subspace of those $u \in W^{p}\Alt^{k}(\Omega)$ 
% for which the extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. }}\todo{MV: repeated below.}
Lastly, we are also interested in differential forms whose trace vanishes along a part of the boundary. 
Suppose that $\Gamma \subseteq \partial\Omega$ is a relatively open subset of the boundary. 
We say that $u \in W^{p}\Alt^{k}(\Omega)$ has vanishing trace along $\Gamma$ if for all $x \in \Gamma$ there exists $r > 0$
% such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(B_r(x))$ we have the integration by parts formula
such that for all $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\bbR^{n})$ 
whose support lies in the open ball $B_r(x)$
we have the integration by parts formula
\begin{align*}
    \int_{B_r(x)} \cartan v \wedge \tilde u
    &=
    (-1)^{k(n-k)+1}
    \int_{B_r(x)} v \wedge \widetilde{\cartan u}
    .
\end{align*}
If that condition is satisfied, we also write 
\begin{align*}
    \trace_{\Gamma} u = 0
    .
\end{align*}
Accordingly, we write $\trace_{\Gamma} u = \trace_{\Gamma} u'$ for $\trace_{\Gamma} (u-u') = 0$ whenever $u, u' \in W^{p}\Alt^{k}(\Omega)$.
Lastly, we introduce the closed subspaces 
\begin{gather*}
    W^{p}_{0}\Alt^{k}(\Omega) 
    := 
    \{ u \in W^{p}\Alt^{k}(\Omega) \suchthat \trace_{\partial \Omega} u = 0 \}
    .
\end{gather*}
% \cye{The space $W^{p}_{0}\Alt^{k}(\Omega)$ formalizes the idea of differential forms with vanishing boundary trace along the boundary $\partial\Omega$.}\todo{MV: Moved here.}
This is a closed subspace. We know that $u \in W^{p}_{0}\Alt^{k}(\Omega)$ if and only if its extension by zero $\tilde u : \bbR^{n} \rightarrow \Alt^{k}(\bbR^{n})$ is a member of $\tilde u \in W^{p}\Alt^{k}(\bbR^{n})$. Moreover, $\cartan W^{p}_{0}\Alt^{k}(\Omega) \subseteq W^{p}_{0}\Alt^{k+1}(\Omega)$. We also observe that $W^{p}\Alt^{n}(\Omega) = W^{p}_{0}\Alt^{n}(\Omega) = L^{p}(\Omega)$. We use the abbreviation $W^{1,p}_{0}(\Omega) := W^{p}\Lambda^{0}(\Omega)$.

@@

\subsection{An operator norm bound with respect to the Lebesgue norm: the Poincar\'e case}

@@

\subsection{An operator norm bound with respect to the Lebesgue norm: the Bogovski\u{\i} case}
